First Order Alternation

### 2018-06-05 quantifiers/draft.tex
ok

For two integers $0 \leq i \leq j$, we denote by $[i,j]$ the set
$\set{i,i+1,\ldots,j}$ and by $[i]$ the set $[1,i]$, where $[0]$ is
the empty set.

A \emph{signature} $\sig = (\ssorts{\sig},\sfuns{\sig})$ consists of a
set $\ssorts{\sig}$ of \emph{sort symbols} and a set $\sfuns{\sig}$ of
sorted \emph{function symbols}. To simplify the presentation, we
assume w.l.o.g. that $\ssorts{\sig} = \set{\Data,\Bool}$\footnote{The
  generalization to more than two sorts is without difficulty, but
  would unnecessarily clutter the technical presentation.} and each
function symbol $f \in \sfuns{\sig}$ has $\#(f) \geq 0$ arguments of
sort $\Data$ and return value of sort $\sort{f}$, which can be either
$\Bool$ or $\Data$. If $\#(f)=0$ then $f$ is a \emph{constant} and we
denote by $\top$ and $\bot$ the only constants of sort $\Bool$,
representing the true and false values, respectively. We write $\preds
= \set{f \in \sfuns{\sig} \mid \sort{f} = \Bool}$ for the set of
boolean function symbols, also called \emph{predicates} in the
following.

We consider an infinite countable set of \emph{variables} $\vars$,
where each $x \in \vars$ has an associated sort, denoted $\sort{x}$. A
\emph{term} $t$ of sort $\sort{t}$ is either a variable $x \in \vars$
of sort $\sort{t}$, or $f(t_1,\ldots,t_{\#(f)})$ where
$t_1,\ldots,t_{\#(f)}$ are terms of sort $\Data$ and
$\sort{f}=\sort{t}$. An \emph{atom} is a term
$p(t_1,\ldots,t_{\#(p)})$ of sort $\Bool$, or an equality $t \teq s$
between two terms of sort $\Data$. A \emph{formula} is a possibly
quantified boolean combination of atoms and a \emph{sentence} is a
formula in which each variable occurs under the scope of a quantifier.
A formula is \emph{positive} if and only if each predicate occurs
under an even number of negations.

We denote by $\fv{\sigma}{\phi}$ the set of free variables of sort
$\sigma$ in $\phi$ and write $\fv{}{\phi}$ for $\bigcup_{\sigma \in
  \ssorts{\sig}} \fv{\sigma}{\phi}$. For a variable $x \in
\fv{}{\phi}$ and a term $t$ such that $\sort{t} = \sort{x}$, let
$\phi[t/x]$ be the result of replacing each occurrence of $x$ by
$t$. For indexed sets $T=\set{t_1,\ldots,t_n}$ and
$X=\set{x_1,\ldots,x_n}$, where $\sort{t_i} = \sort{x_i}$, we write
$\phi[T/X]$ for the formula obtained by simultaneously replacing $x_i$
with $t_i$ in $\phi$, for all $i\in[n]$. The size $\len{\phi}$ is the
number of symbols occuring in $\phi$.

An \emph{interpretation} $\I$ maps \begin{inparaenum}[(1)]
\item the sort $\Data$ into a non-empty set $\Data^\I$, 
%
\item the sort $\Bool$ into the set $\booli = \set{\true,\false}$, where
  $\top^\I = \true$, $\bot^\I = \false$, and
%
\item each function symbol $f$ into a total function $f^\I :
  \left(\Data^\I\right)^{\#(f)} \rightarrow \sort{f}^I$, or an element
  of $\sort{f}^I$ when $\#(f)=0$.
\end{inparaenum}
Given an interpretation $\I$, a \emph{valuation} $\nu$ maps each
variable $x \in \vars$ into an element of $x_\sigma^\I$. For a term
$t$, we denote by $t^\I_\nu$ the value obtained by replacing each
function symbol $f$ by its interpretation $f^\I$ and each variable $x$
by its valuation $\nu(x)$. For a formula $\phi$, we write $\I,\nu
\models \phi$ if the formula obtained by replacing each term $t$ in
$\phi$ by the value $t^\I_\nu$ is logically equivalent to true.  The
semantics of quantifiers is given as usual: $\I,\nu \models \exists x
~.~ \phi$ if and only if $\I,\nu[x \leftarrow u] \models \phi$, for
some value $u \in \sort{x}^\I$, where $\nu[x \leftarrow u]$ is the
valuation that assigns $u$ to $x$ and $\nu(y)$ to all $y \neq x$.

A formula $\phi$ is \emph{satisfiable} in the interpretation $\I$ if
there exists a valuation $\nu$ such that $\I,\nu \models \phi$, and
\emph{valid} if $\I,\nu \models \phi$ for all valuations $\nu$.  The
\emph{first-order theory} $\theory(\sig,\I)$ is the set of valid
formulae written in the signature $\sig$, with the interpretation
$\I$. A \emph{decision procedure} for $\theory(\sig,\I)$ is an
algorithm that takes a formula $\phi$ in the signature $\sig$ and
returns yes if and only if $\phi \in \theory(\sig,\I)$.

Given formulae $\varphi$ and $\psi$, we say that \emph{$\phi$ entails
  $\psi$ modulo $\theory(\sig,\I)$}, denoted $\phi
\models_{\theory(\sig,\I)} \psi$ iff $\varphi \rightarrow \psi \in
\theory(\sig,\I)$. We say that $\varphi$ and $\psi$ are
\emph{$\theory(\sig,\I)$-equivalent}, denoted $\phi
\equiv_{\theory(\sig,\I)} \psi$ iff $\phi \models_{\theory(\sig,\I)}
\psi$ and $\psi \models_{\theory(\sig,\I)} \phi$. The theory
$\theory(\sig,\I)$ has \emph{quantifier elimination} iff for any
formula $\exists x ~.~ \phi(x)$, where $\phi$ is quantifier-free,
there exists a quantifier free formula $\psi$ such that $\phi$ and
$\psi$ are $\theory(\sig,\I)$-equivalent.

\section{First Order Alternating Data Automata}

In the rest of the paper, we we fix a theory $\theory(\sig,\I)$ and
omit mentioning it in the context of entailments and equivalences. Let
$\Sigma$ be a finite alphabet $\Sigma$ of \emph{input events}. Given a
finite set $X \subset \vars$ of variables of sort $\Data$, we denote
by $X \mapsto \Data^\I$ the set of valuations of the variables $X$ and
$\Sigma[X] = \Sigma \times (X \mapsto \Data^\I)$ be the possibly
infinite set of \emph{data symbols}. A \emph{data word} (word in the
sequel) is a finite sequence $(a_1,\nu_1)(a_2,\nu_2) \ldots
(a_n,\nu_n)$ of data symbols, where $a_1,\ldots,a_n \in \Sigma$ and
$\nu_1,\ldots,\nu_n : X \rightarrow \Data^\I$ are valuations. We
denote by $\varepsilon$ the empty sequence, by $\Sigma^*$ the set of
finite sequences of input events and by $\Sigma[X]^*$ the set of data
words over the variables $X$.

A \emph{first-order alternating data automaton} (automaton in the
sequel) is a tuple $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$, where
$\Sigma$ is the finite event alphabet, $X$ is a
finite set of variables, $Q \subseteq \preds$ is a finite set of
\emph{state predicates}, $\iota$ is a sentence, $F \subseteq Q$ is a
set of \emph{final states} and $\Delta$ is a set of \emph{transition
  rules} of the form:
\[q(y_1,\ldots,y_{\#(q)}) \arrow{a(X)}{} \psi\]
where $q \in Q$, $a \in \Sigma$, $\psi$ is a positive formula such
that $\fv{}{\phi} \subseteq X \cup \set{y_1,\ldots,y_{\#(q)}}$, $X
\cap \set{y_1,\ldots,y_{\#(q)}} = \emptyset$ and each predicate that
occurs in $\psi$ belongs also to $Q$. We stress the fact that each
predicate occurs in $\psi$ under an even number of negations.

Intuitively, $a$ is the input event and $X$ are the input data values
that trigger the transition, whereas $q$ and $y_1,\ldots,y_{\#(q)}$
are the current control state and data values pertaining to that
state, respectively. Without loss of generality, we consider, for each
predicate $q \in Q$ and each input event $a \in \Sigma$, at most one
such rule (two or more rules can be joined using disjunction). The
\emph{size} of $\A$ is defined as $\len{\A} = \len{\iota} +
\sum_{q(\vec{y}) \arrow{a(X)}{} \psi \in \Delta} \len{\psi}$.

@@

To simplify the presentation, at this point, we shall give the
execution semantics of automata in terms of symbolic rewriting rules.
The connection between this symbolic semantics and the concrete
semantics, expressed in terms of sets of configurations, will be given
at a later time. Let $\stamp{X}{i} = \set{\stamp{x}{i} \mid x \in X}$
be a set of \emph{time-stamped} variables. For a formula $\psi$ and $i
\in \nat$, we define $\stamp{\psi}{i} = \psi[X/\stamp{X}{i}]$,
i.e.\ the formula in which each variable $x \in X$, denoting an input
data element, is replaced by $\stamp{x}{i}$. Further, given a formula
$\phi$, let $\Accept{F}{\phi}$ be the formula obtained from $\phi$ by
replacing each predicate atom $q(z_1,\ldots,z_{\#(q)})$ by $\top$ if
$q \in F$, and by $\bot$, otherwise.

For an input word $(a_1,\nu_1) \ldots (a_n,\nu_n) \in \Sigma[X]^*$,
we define the sequence of formulae \(\phi_0 \Rightarrow \phi_1
\Rightarrow \ldots \Rightarrow \phi_n\), where $\phi_0 = \iota$ and
$\phi_{i+1}$ is obtained from $\phi_i$ by replacing each predicate
atom $q(z_1,\ldots,z_{\#(q)})$ from $\phi_i$ by the formula
$\stamp{\psi}{i+1}[z_1, \ldots, z_{\#(q)}/y_1,\ldots,y_{\#(q)}]$,
where $q(y_1,\ldots,y_{\#(q)}) \arrow{a_i(X)}{} \psi \in \Delta$ is
the only transition rule that applies, or by $\bot$, if no transition
rule applies. Observe that $\phi_n$ is uniquely defined by the event
sequence $a_1 \ldots a_n \in \Sigma^*$. The word $(a_1,\nu_1) \ldots
(a_n,\nu_n)$ is \emph{accepted} by $\A$ if and only if $\I,\nu \models
\Accept{F}{\phi_n}$, where the valuation $\nu : \bigcup_{i=1}^n
\stamp{X}{i} \rightarrow \Data^\I$ is defined as $\nu(\stamp{x}{i}) =
\nu_i(x)$, for each $x \in X$ and $i \in [n]$.

As usual, the \emph{language} of $\A$, denoted $\lang{\A}$, is the set
of words accepted by $\A$. In this paper, we ask the following
questions: \begin{compactenum}
\item \emph{closure}: given automata $\A_i =
  \tuple{\Sigma,X,Q_i,\iota_i,F_i,\Delta_i}$, for $i=1,2$, do there
  exist automata $\A_\cap$, $\A_\cup$ and $\overline{\A}_1$ such that
  $L(\A_\cap) = L(\A_1) \cap L(\A_2)$, $L(\A_\cup) = L(\A_1) \cup
  L(\A_2)$ and $L(\overline{\A}_1) = \Sigma[X]^* \setminus L(\A_1)$ ?
%
\item \emph{emptiness}: given an automaton $\A$, is $L(\A) =
  \emptyset$?
\end{compactenum}

>>>>

For two integers $0 \leq i \leq j$, we denote by $[i,j]$ the set
$\set{i,i+1,\ldots,j}$ and by $[i]$ the set $[1,i]$, where $[0]$ is
the empty set. To simplify the presentation, we consider two sorts
$\Data$ and $\Bool$, where $\Data$ ranges over an infinite domain and
$\Bool$ has the usual interpretation. The $\Data$ sort is equipped
with a finite set of function symbols $f : \Data^{\#(f)} \rightarrow
\Data$, where $\#(f)\geq0$ denotes the number of arguments (arity) of
$f$. When $\#(f)=0$, we say that $f$ is a constant, and denote by
$\top$ and $\bot$ the only constants of sort $\Bool$, representing the
true and false values, respectively.  For conciseness, in the
following we blur the distinction between the sort and function
symbols and their interpretations. A \emph{predicate} is a function
symbol $p : \Data^{\#(p)} \rightarrow \Bool$, denoting a relation of
arity $\#(p)$.

Let $\vars = \set{x,y,z,\ldots}$ be an infinite countable set of
variables, ranging over the interpretation of the $\Data$ sort. Terms
are either constants of sort $\Data$, variables or function
applications. The set of \emph{positive} formulae is defined by the
syntax below: 
\[\phi := t \teq s \mid t \not\teq s \mid p(t_1,\ldots,t_{\#(p)}) 
\mid \phi_1 \wedge \phi_2 \mid \phi_1 \vee \phi_2 \mid \exists x ~.~
\phi_1 \mid \forall x ~.~ \phi_1\] where $t,s,t_1,\ldots,t_{\#(p)}$
denote terms. We denote by $\fv{}{\phi}$ the set of free variables in
$\phi$. A \emph{sentence} is a formula $\phi$ in which each variable
occurs under the scope of a quantifier, i.e. $\fv{}{\phi} =
\emptyset$. The size $\len{\phi}$ is the number of symbols occuring in
$\phi$.

%% For a variable $x \in \fv{}{\phi}$ and a term $t$, let $\phi[t/x]$ be
%% the result of replacing each occurrence of $x$ by $t$. For indexed
%% sets of terms $T=\set{t_1,\ldots,t_n}$ and variables
%% $X=\set{x_1,\ldots,x_n}$, we write $\phi[T/X]$ for the formula
%% obtained by simultaneously replacing each occurrence of $x_i$ with
%% $t_i$ in $\phi$, for all $i\in[n]$.

An \emph{interpretation} $\I$ maps each predicate $p$ into a set $p^\I
\subseteq \Data^{\#(p)}$, if $\#(p)>0$, or into an element of $\Data$
if $\#(p)=0$. A \emph{valuation} $\nu$ maps each variable $x$ into an
element of $\Data$. Given a term $t$, we denote by $t^\nu$ the value
obtained by replacing each variable $x$ by the value $\nu(x)$ and
evaluating each function application. For a formula $\phi$, we define
the forcing relation $\I,\nu \models \phi$ recursively on the
structure of $\phi$, as follows:
\[
\begin{array}{rcl}
\I,\nu \models t \teq s & \iff & t^\nu=s^\nu \\
\I,\nu \models t \not\teq s & \iff & t^\nu \neq s^\nu \\
\I,\nu \models \phi_1 \wedge \phi_2 & \iff & \I,\nu \models \phi_i \text{, for all } i=1,2 \\ 
\I,\nu \models \phi_1 \vee \phi_2 & \iff & \I,\nu \models \phi_i \text{, for some } i=1,2 \\
\I,\nu \models \forall x ~.~ \phi_1 & \iff & \I,\nu[x\leftarrow d] \models \phi_1 \text{, for all } d \in \Data \\
\I,\nu \models \exists x ~.~ \phi_1 & \iff & \I,\nu[x\leftarrow d] \models \phi_1 \text{, for some } d \in \Data \\
\I,\nu \models p(t_1,\ldots,t_{\#(p)}) & \iff & \tuple{t_1^\nu,\ldots,t_{\#(p)}^\nu} \in p^\I 
\end{array}
\]
For a formula $\phi$, we define $\sem{\phi}_\nu \isdef \set{\I \mid
  \I,\nu \models \phi}$, where $\nu(x)$ is defined for each $x \in
\fv{}{\phi}$, and drop the subscript for sentences. An element of
$\sem{\phi}$ is called a \emph{model} of $\phi$. A formula is
satisfiable if $\sem{\phi}\neq\emptyset$.

\section{First Order Alternating Automata}

Let $\Sigma$ be a finite alphabet $\Sigma$ of \emph{input
  events}. Given a finite set of variables $X$, we denote by $X
\mapsto \Data^\I$ the set of valuations of the variables $X$ and
$\Sigma[X] = \Sigma \times (X \mapsto \Data)$ be the possibly infinite
set of \emph{data symbols}. A \emph{data word} (word) is a finite
sequence $(a_1,\nu_1)(a_2,\nu_2) \ldots (a_n,\nu_n)$ of data symbols,
where $a_1,\ldots,a_n \in \Sigma$ and $\nu_1,\ldots,\nu_n : X
\rightarrow \Data$ are valuations. We denote by $\varepsilon$ the
empty sequence, by $\Sigma^*$ the set of finite sequences of input
events and by $\Sigma[X]^*$ the set of data words over the variables
$X$.

A \emph{first-order alternating automaton} (automaton) is a tuple $\A
= \tuple{\Sigma,X,Q,\iota,F,\Delta}$, where $\Sigma$ is the finite
event alphabet, $X$ is a finite set of variables, $Q$ is a finite set
of predicates, $\iota$ is a satisfiable sentence, $F \subseteq Q$ is a
set of \emph{final predicates} and $\Delta$ is a set of
\emph{transition rules} of the form \(q(y_1,\ldots,y_{\#(q)})
\arrow{a(X)}{} \psi\), where $q \in Q$ is a predicate, $a \in \Sigma$
is an input event, $X \cap \set{y_1,\ldots,y_{\#(q)}} = \emptyset$,
$\psi$ is a positive formula such that $\fv{}{\phi} \subseteq X \cup
\set{y_1,\ldots,y_{\#(q)}}$ and each predicate that occurs in $\psi$
belongs also to $Q$. The \emph{size} of $\A$ is defined as $\len{\A} =
\len{\iota} + \sum_{q(\vec{y}) \arrow{a(X)}{} \psi \in \Delta}
\len{\psi}$.

Intuitively, $a$ is the input event and $X$ are the input data values
that trigger the transition, whereas $q$ and $y_1,\ldots,y_{\#(q)}$
are the current control state and data values pertaining to that
state, respectively. Without loss of generality, we consider, for each
predicate $q \in Q$ and each input event $a \in \Sigma$, at most one
such rule (two or more rules can be joined using disjunction).

@@

To formalize the execution semantics of automata, we relate sets of
configurations to models of first-order sentences, as follows. Given a
formula $\phi$ and a valuation of its free variables $\nu$, each
interpretation $\I \in \sem{\phi}_\nu$ corresponds to a set of
configurations $\cube{\I} \isdef \set{q(d_1,\ldots,d_{\#(q)}) \mid
  \tuple{d_1,\ldots,d_{\#(q)}} \in q^\I}$, called a \emph{cube}. For a
set $\mathcal{M}$ of interpretations, we define $\cube{\mathcal{M}}
\isdef \set{\cube{\I} \mid \I \in \mathcal{M}}$.

Given a word $w=(a_1,\nu_1)(a_2,\nu_2) \ldots (a_n,\nu_n) \in
\Sigma[X]^*$, an \emph{execution} of
$\A=\tuple{\Sigma,X,Q,\iota,F,\Delta}$ over $w$ is a (possibly
infinite) forest $\F_w = \set{T_1,T_2,\ldots}$, where each $T_i$ is
defined below:
\begin{compactitem}
\item $T_i$ is rooted in a configuration from some cube $C \in
  \cube{\sem{\iota}}$ --- since $\iota$ is satisfiable, such cube
  always exists,
%
\item all paths from the root to a leaf of $T_i$ have length $n$,
%
\item if $q(d_1,\ldots,d_{\#(q)})$ is a node on level $j \in [0,n-1]$
  in $T_i$, then its children form a cube $C \in
  \cube{\sem{\psi}_\eta}$, where \(q(y_1,\ldots,y_{\#(q)})
  \arrow{a_{j+1}(X)}{} \psi \in \Delta\) is a transition rule and
  $\eta$ is a valuation that assigns each variable $y_k$ the value
  $d_k$, for $k \in [1,\#(q)]$ and each variable $x \in X$ the value
  $\nu_{j+1}(x)$ --- because $\fv{}{\psi} \subseteq
  \set{y_1,\ldots,y_{\#(q)}} \cup X$, the values assigned by $\eta$ to
  variables outside $\set{y_1,\ldots,y_{\#(q)}} \cup X$ are not
  important for $\cube{\sem{\psi}_\eta}$.
\end{compactitem}
A forest $\F_w$ is said to be \emph{accepting} if and only if the
frontier of each tree $T \in \F_w$ is labeled with configurations
$q(d_1,\ldots,d_{\#(q)})$ such that $q \in F$ is a final predicate. In
this case, we say that $\A$ accepts $w$ and denote by $\lang{\A}$ the
set of words accepted by $\A$. In this paper, we answer the following
questions: \begin{compactenum}
\item \emph{closure}: given automata $\A_i =
  \tuple{\Sigma,X,Q_i,\iota_i,F_i,\Delta_i}$, for $i=1,2$, do there
  exist automata $\A_\cap$, $\A_\cup$ and $\overline{\A}_1$ such that
  $L(\A_\cap) = L(\A_1) \cap L(\A_2)$, $L(\A_\cup) = L(\A_1) \cup
  L(\A_2)$ and $L(\overline{\A}_1) = \Sigma[X]^* \setminus L(\A_1)$ ?
%
\item \emph{emptiness}: given an automaton $\A$, is $L(\A) =
  \emptyset$?
\end{compactenum}

\subsection{Symbolic Execution}

In several of the upcoming developments it is more convenient to work
with a symbolic execution semantics, that describes a set of execution
forests by a sequence of formulae obtained one from another using
rewriting rules. Let $\A = \tuple{\Sigma,X,Q,\iota,F,\Delta}$ be an
automaton and $\stamp{X}{i} = \set{\stamp{x}{i} \mid x \in X}$ be a
set of \emph{time-stamped} variables. For a formula $\psi$ and $i \in
\nat$, we define $\stamp{\psi}{i} = \psi[X/\stamp{X}{i}]$, i.e.\ the
formula in which each variable $x \in X$, denoting an input data
element, is replaced by $\stamp{x}{i}$. Further, given a formula
$\phi$, let $\Accept{F}{\phi}$ be the formula obtained from $\phi$ by
replacing each predicate atom $q(z_1,\ldots,z_{\#(q)})$ by $\top$ if
$q \in F$, and by $\bot$, otherwise.

For a sequence of input events $a_1 \ldots a_n \in \Sigma^*$, we
consider the sequence of formulae \(\phi_0 \stackrel{a_1}{\Rightarrow}
\phi_1 \stackrel{a_2}{\Rightarrow} \ldots \stackrel{a_n}{\Rightarrow}
\phi_n\), where $\phi_0 = \iota$ and $\phi_{i+1}$ is obtained from
$\phi_i$ by replacing each predicate atom $q(t_1,\ldots,t_{\#(q)})$
from $\phi_i$ by the formula $\stamp{\psi}{i+1}[t_1, \ldots,
  t_{\#(q)}/y_1,\ldots,y_{\#(q)}]$, where $q(y_1,\ldots,y_{\#(q)})
\arrow{a_i(X)}{} \psi \in \Delta$ is the only transition rule that
applies, or by $\bot$, if no transition rule applies. The following
lemma formalizes the relation between symbolic execution and the
low-level configuration-based semantics of automata:

\begin{lemma}\label{lemma:symbolic-execution}
  A word $(a_1,\nu_1) \ldots (a_n,\nu_n)$ is accepted by $\A =
  \tuple{\Sigma,X,Q,\iota,F,\Delta}$ if and only if $\I,\nu \models
  \Accept{F}{\phi_n}$ for each interpretation $\I$, where the
  valuation $\nu : \bigcup_{i=1}^n \stamp{X}{i} \rightarrow \Data$ is
  defined as $\nu(\stamp{x}{i}) = \nu_i(x)$, for each $x \in X$ and $i
  \in [n]$.
\end{lemma}
\proof{ ``$\Rightarrow$'' Assume that $w = (a_1,\nu_1) \ldots
  (a_n,\nu_n)$ is accepted by $\A$ and let $\F_w$ be an execution
  forest of $\A$ over $w$. First, it is easy to check that $\phi_i$ is
  a positive formula, for each $i \in [n]$. Next, we define the
  interpretation: \[\I^w_n(q) = \set{\tuple{d_1,\ldots,d_{\#(q)}} \mid
    q(d_1,\ldots,d_{\#(q)}) \text{ occurs on the $n$-th level of }
    F_w}\] and prove $\I^w_n,\nu \models \phi_n$, by induction on
  $n\geq0$. For $n=0$, we have $\cube{\I^w_0} \in
  \cube{\sem{\iota}}$ and $\I^w_0 \models \iota$ follows, by
  definition. For the induction step, assume that $\I^w_{n-1},\mu
  \models \phi_{n-1}$, where $\mu(\stamp{x}{i}) = \nu_i(x)$, for each
  $x \in X$ and $i \in [n-1]$.

  \noindent''$\Leftarrow$'' 
\qed}
